Leveraging Semantics for a Deep Web Question and Answering System

### 2010-02-22 paper/semsearch10/paper.tex
latest

\title{Leveraging Semantics for a Deep Web Question and Answering System} 
\numberofauthors{5}
\author{
	\alignauthor Christan Grant\\
	\email{cgrant@cise.ufl.edu}

@@

@@

\begin{abstract}
\end{abstract}

@@

\section{Introduction}
% Christan

>>>>

\title{Leveraging Semantics for a Deep Web Question and Answering System} 
\numberofauthors{7}
\author{
	\alignauthor Christan Grant\\
	\email{cgrant@cise.ufl.edu}

@@

	\alignauthor Peter J. Dobbins\\
	\email{pjd@cise.ufl.edu}

	\alignauthor Jeff T. Depree\\
	\email{jepree@cise.ufl.edu}

@@

\begin{abstract}
- It is difficult to answer question that change over time
- However, if the method of answering the question can be realized, the question can be easily answered
- We are building a system that supports a learning how to answer particular questions
- We can answer questions that are semantically similar to our store of questions
- We do this by building a semantic library ...
\end{abstract}

@@

\section{Introduction}
% Christan
- The best way to answer questions is to see/know if a question has been asked before.
- IEEE potentials talks about the the beaten trail.
- Use reuse in the specific domain of question answering
